|

### 2020-05-15 _support/docu/fs_comment.tex
timelime improvements, bold symbol, etc. revealjs tests.

\documentclass{article}

\usepackage{blindtext}
\usepackage{multicol}
\usepackage{caption}
\usepackage{bm}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}
\usepackage{geometry}
\geometry{
	a4paper,
	noheadfoot=true,
	left=1.0in,
	right=1.0in,
	top=1.0in,
	bottom=1.0in
}

% url package
\usepackage{hyperref}
\usepackage{subcaption}

% Titling and Author
\title{Latex Tikz Examples, Annotate on Graph}
\author{\href{https://fanwangecon.github.io/}{Fan Wang}\thanks{https://fanwangecon.github.io, repository: \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ}}}
\date{\today}

@@

\maketitle

\section{Annotate Text in Figure}

\subsection{Slope and Intercept Annotate}

Draw axis below, and a line, middle of page, and annotate the slope of the intercept with arrows. Annotate with box without color.

\begin{verbatim}
\begin{center}
\begin{tikzpicture}
\draw (0,2) -- (0.25*\textwidth,2);
\draw (0,1) -- (0.5*\textwidth,1);
\end{tikzpicture}
\end{center}
\end{verbatim}
\bigskip
\begin{center}
\begin{tikzpicture}
\draw[->] (-1,0) -- (6,0) node[right] {$N_m$};
\draw[->] (0,-1) -- (0,6) node[above] {$N_{m^{\prime}}$};

% A. Clip area so that line below is only drawn inside finite box
\clip (-3,-1) rectangle (6,6);

% B. Draw a line with intercept and slope
\draw[line width=0.50mm,domain=-1:6,smooth,variable=\x, blue] plot ({\x},{1+\x*1.25});

% C. Draw Line pointing to Intercept of line
\draw[->, line width=0.75mm] (-1.7,2.2) -- (-0.1,1.1);

% D. Draw a transparent text box that wraps text
\node[text width=3cm] at (-1.4,3.25) {\large{$\bm{\alpha_i}$ (this is the position of the \textbf{x-intercept}), wrap text.}};

\end{tikzpicture}
\end{center}

\subsection{Anote Slope, X intercept and Y intercept}

Draw a line, then point to its slope, x and y intercepts.

\begin{enumerate}
  \item Define the slope and y-intercept: $a_i, b_i$
  \item Define and calculate the x-intercept: $c_i = -\frac{a_i}{b_i}$
  \item Define the text that should appear for each element: $a_{desca}$
  \item Drawing lines pointing to $a$, $b$ or $c$ points:
  \begin{itemize}
    \item direction: $d_i \in \left\{NE, SE, SW, NW\right\}$
    \item rotation: $0 <= e_i <= 90$, which direction points to text
    \item dist one: $f_i > 0 $, straight distance from origin
    \item dist two: $g_i > 0 $, distance of line
    \item point start: $h^o_i, h^o_i$, starting point based on the four pieces of information
    \item point end: $h^d_i, h^d_i$, ending point based on the four pieces of information
  \end{itemize}
\end{enumerate}

So end up drawing using $a$, $b$ for line, $h^o$ for one point $h*d$ line small segment.

\begin{verbatim}
\end{verbatim}
\bigskip
\begin{center}
\begin{tikzpicture}
\draw[->] (-1,0) -- (6,0) node[right] {$N_m$};
\draw[->] (0,-1) -- (0,6) node[above] {$N_{m^{\prime}}$};

% A. Clip area so that line below is only drawn inside finite box
\clip (-3,-1) rectangle (6,6);

% B. Draw a line with intercept and slope
\draw[line width=0.50mm,domain=-1:6,smooth,variable=\x, blue] plot ({\x},{1+\x*1.25});

% C. Draw Line pointing to Intercept of line
\draw[->, line width=0.75mm] (-1.7,2.2) -- (-0.1,1.1);

% D. Draw a transparent text box that wraps text
\node[text width=3cm] at (-1.4,3.25) {\large{$\bm{\alpha_i}$ (this is the position of the \textbf{x-intercept}), wrap text.}};

\end{tikzpicture}
\end{center}

>>>>

\documentclass[12pt,english]{article}
\usepackage[utf8]{inputenc}

% url package
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}
% Bibliography package
\usepackage[authordate, backend=biber]{biblatex-chicago}
\bibliography{fansample}

% Titling and Author
\title{Latex Preamble}
\author{\href{https://fanwangecon.github.io/}{Fan Wang}\thanks{https://fanwangecon.github.io, repository: \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ}}}
\date{\today}

@@

Comment will not appear with percent in front

\begin{verbatim}
% Comment
\end{verbatim}
% Comment

yml block?

\begin{verbatim}
<!-- regular html comment -->
\end{verbatim}

<!-- regular html comment -->

### 2020-05-15 nontex/install/windows/fn_installations.Rmd
timelime improvements, bold symbol, etc. revealjs tests.

@@

### Sublime

@@

#### Sublime and Outline (Markdown)

@@

#### Sublime Search and Replace

@@

### PyCharm

@@

@@

- [pandoc](https://pandoc.org/installing.html)
- 7-zip
- evernote

>>>>

#### Conda revealjs nodejs Environment

revealjs, decktape to pdf conversions

```{r}
# Set up
conda deactivate
conda list env
conda env remove -n wk_nodejs
conda create -n wk_nodejs -y
conda activate wk_nodejs

conda install -c conda-forge nodejs -y
# ended up downloading installer for windows nodejs and installing out of conda
# was having lots of bugs
npm i -g --production windows-build-tools
npm install -g --force decktape
# use yaml2tex

cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\repos\fanwangecon.github.io\_cv\templating\"
python yaml2tex.py
```

@@

## Sublime

@@

### Sublime and Outline (Markdown)

@@

### Sublime Search and Replace

@@

## PyCharm

@@

### PyCharm Short Cuts

- Auto-Indent: *CTRL + SHIFT + ALT + L*

@@

- [pandoc](https://pandoc.org/installing.html)
- [nodejs](https://nodejs.org/en/) (revealjs pdf conversion)
- 7-zip
- evernote
